---
title: "Holt-Winters Model"
author: "GroupA"
date: "1/19/2022"
---


1.  Select one time series from data_week.csv
2.  Try the four combinations of beta and gamma as on/off
3.  Present the plots of data series, trend, and seasonal components, and check residuals for each of the four combinations
4.  Make out-of-sample forecast for 26 weeks with confidence bands.
5.  Recommend one forecasting model -- give your justification

```{r}
data<-read.csv("data_week.csv", sep=",",dec=".",header=T) 	# weekly data

library("forecast")	
```

## Metric 1: online budget - by Joyce Chen

```{r}
yy <- ts(data$online_budget, frequency = 52, start = c(2015, 1))
plot.ts(yy)  
```

```{r}
##### Time Series Decomposition  #####
budget <- decompose(yy)
budget.trend = budget$trend
budget.seasonal = budget$seasonal
budget.resid = budget$random
budget.season.adj = yy - budget.seasonal									# seasonally adjusted sales
plot.ts(cbind(yy,budget.trend, budget.seasonal, budget.resid, budget.season.adj))

```

```{r}
##### Holt-Winters Filter  #####
#### Combination 1: beta = TRUE, gamma = TRUE
out1 = HoltWinters(yy, beta = TRUE, gamma = TRUE) 				# Holt-Winters Filtering - only level updating b/c beta and gamma are zeros
out1														# output -- see alpha estimate
out1$fitted 												# fitted values in training data
plot(out1)													# graph of actual (black) vs fitted (red)

##### Check Residuals
checkresiduals(out1)

##### Out of Sample Forecasts
out1a = forecast:::forecast.HoltWinters(out1, h = 26, level = c(68, 95))	 
# forecast horizon 26 weeks. 
# level = c(68, 95) - CI with 1 SD and 2SD
plot(out1a)
```

```{r}
#### Combination 2: beta = TRUE, gamma = FALSE
out2 = HoltWinters(yy, beta = TRUE, gamma = FALSE) 				
out2													
out2$fitted 											
plot(out2)													

##### Check Residuals
checkresiduals(out2)

##### Out of Sample Forecasts
out2a = forecast:::forecast.HoltWinters(out2, h = 26, level = c(68, 95))	 
plot(out2a)
```

```{r}
#### Combination 3: beta = FALSE, gamma = TRUE
out3 = HoltWinters(yy, beta = FALSE, gamma = TRUE) 				
out3													
out3$fitted 											
plot(out3)													

##### Check Residuals
checkresiduals(out3)

##### Out of Sample Forecasts
out3a = forecast:::forecast.HoltWinters(out3, h = 26, level = c(68, 95))	 
plot(out3a)
```

```{r}
#### Combination 4: beta = FALSE, gamma = FALSE
out4 = HoltWinters(yy, beta = FALSE, gamma = FALSE) 				
out4													
out4$fitted 											
plot(out4)													

##### Check Residuals
checkresiduals(out4)

##### Out of Sample Forecasts
out4a = forecast:::forecast.HoltWinters(out4, h = 26, level = c(68, 95))	 
plot(out4a)
```

### Model Selection

1.  Comparing the plots of the forecasts with different confidence intervals, the first one and the third one show similar pattern as the previous periods. The last combination without trend and seasonality shows a flat line, which apparently does not conform with the previous pattern. The second combination with trend but no seasonality shows a line going downward, which the previous pattern roughly goes horizontal.
2.  Then comparing the first and the third combinations, both the residual checks show slight systematic patterns. However, by carefully evaluating the forecast plots, we conclude the third one is a better fit.
3.  Therefore, regarding online budget, we select the model with seasonality and with no trend as the best forecasting model.

## Metric 2: direct_emails - by Kexin Fu

```{r}
dmails = data[,4]/1000		# thousands in xyz currency

##### Representing Data as Time Series Objects #####

yy = ts(dmails, frequency = 52,start = c(2015,1)) # coverts sales data as time series object with start date and weekly frequency
plot.ts(yy)									# ALWAYS plot time series to see patterns: trend, cycle, variance over time
```

```{r}
## Trend and Seasonal Components of the original
dimail_d = decompose(yy) 
dimail.trend = dimail_d$trend
dimail.seasonal = dimail_d$seasonal
dimail.resid = dimail_d$random
dimail.season.adj = yy - dimail.seasonal									# seasonally adjusted sales
plot.ts(cbind(yy,dimail.trend, dimail.seasonal, dimail.resid, dimail.season.adj))
```

```{r}
##### Holt-Winters Filter  #####

# 1. Beta = T, Gamma = T

out1 = HoltWinters(yy, beta = T, gamma = T) 				# Holt-Winters Filtering - only level updating b/c beta and gamma are zeros
out1														# output -- see alpha estimate
out1$fitted 												# fitted values in training data
plot(out1)													# graph of actual (black) vs fitted (red)

##### Check Residuals
checkresiduals(out1)

# 2. Beta = T, Gamma = F

out2 = HoltWinters(yy, beta = T, gamma = F) 				# Holt-Winters Filtering - only level updating b/c beta and gamma are zeros
out2														# output -- see alpha estimate
out2$fitted 												# fitted values in training data
plot(out2)													# graph of actual (black) vs fitted (red)

##### Check Residuals
checkresiduals(out2)

# 3. Beta = F, Gamma = T

out3 = HoltWinters(yy, beta = F, gamma = T) 				# Holt-Winters Filtering - only level updating b/c beta and gamma are zeros
out3														# output -- see alpha estimate
out3$fitted 												# fitted values in training data
plot(out3)													# graph of actual (black) vs fitted (red)

##### Check Residuals
checkresiduals(out3)

# 4. Beta = F, Gamma = F

out4 = HoltWinters(yy, beta = F, gamma = F) 				# Holt-Winters Filtering - only level updating b/c beta and gamma are zeros
out4														# output -- see alpha estimate
out4$fitted 												# fitted values in training data
plot(out4)													# graph of actual (black) vs fitted (red)

##### Check Residuals
checkresiduals(out4)
```

```{r}
##### Out of Sample Forecasts

							# install "forecast" package and load the library		
result1 = forecast:::forecast.HoltWinters(out1, h = 26, level = c(68, 95))	 
plot(result1)

result2 = forecast:::forecast.HoltWinters(out2, h = 26, level = c(68, 95))	 
plot(result2)

result3 = forecast:::forecast.HoltWinters(out3, h = 26, level = c(68, 95))	 
plot(result3)

result4 = forecast:::forecast.HoltWinters(out4, h = 26, level = c(68, 95))	 
plot(result4)

```

### Model Selection

I will recommend the forecast model with beta = T and gamma = T. The overall fitting looks well. Residuals look random.

And gamma = T models fit much better than gamma = F models by looking the fitting plots, since there is clear seasonality in the decompose graph as well.

Moreover,the decompose graph shows clear upward trend. So the beta is also set to T.

## Metric 3: promotion - by Yutian Lei

```{r}
promotion = data$promotion		# categorical variable for promotion

##### Representing Data as Time Series Objects #####
xx = ts(promotion, frequency = 52, start = c(2015,1))
plot.ts(xx,ylab = "promotion")
```

```{r}
##### Time Series Decomposition  #####
promo = decompose(xx) 
promo.trend = promo$trend
promo.seasonal = promo$seasonal
promo.resid = promo$random
promo.season.adj = xx - promo.seasonal			
plot.ts(cbind(xx,promo.trend, promo.seasonal, promo.resid, promo.season.adj))
```

```{r}
# Try the four combinations of beta and gamma as on/off
##### Holt-Winters Filter  #####
tt = HoltWinters(xx, beta = TRUE, gamma = TRUE)
tf = HoltWinters(xx, beta = TRUE, gamma = FALSE)
ft = HoltWinters(xx, beta = FALSE, gamma = TRUE)
ff = HoltWinters(xx, beta = FALSE, gamma = FALSE)

# graph of actual (black) vs fitted (red)
plot(tt)													
plot(tf)													
plot(ft)													
plot(ff)													
```

```{r}
##### Check Residuals
checkresiduals(tt)
checkresiduals(tf)
checkresiduals(ft)
checkresiduals(ff)
```

```{r}
# forecast horizon 26 weeks, CI with 1 SD and 2SD
forecast_tt = forecast:::forecast.HoltWinters(tt, h = 26, level = c(68, 95))
plot(forecast_tt)

forecast_tf = forecast:::forecast.HoltWinters(tf, h = 26, level = c(68, 95))
plot(forecast_tf)

forecast_ft = forecast:::forecast.HoltWinters(ft, h = 26, level = c(68, 95))
plot(forecast_ft)

forecast_ff = forecast:::forecast.HoltWinters(ff, h = 26, level = c(68, 95))
plot(forecast_ff)
```

### Model Selection

I would recommend the combination where beta is off and gamma is on for the following reasons:\
- From the graph of actual (black) vs fitted (red), this forecast model mostly fitted the actual values.\
- From the residual plot, residuals are in a constant interval. ACF graph looks good with only one outside of the confidence bound. The residuals are nearly normally distributed.

## Metric 4: wind_speed - Yucheng Jiang

```{r}
wind_speed = data[,12]

##### Representing Data as Time Series Objects #####
ts_wind_speed = ts(wind_speed, frequency = 52, start = c(2015,1))
plot.ts(ts_wind_speed)
```

```{r}
##### Time Series Decomposition  #####
wind_speed_d <- decompose(ts_wind_speed)
wind_speed_d.trend = wind_speed_d$trend
wind_speed_d.seasonal = wind_speed_d$seasonal
wind_speed_d.resid = wind_speed_d$random
wind_speed_d.season.adj = ts_wind_speed - wind_speed_d.seasonal	# seasonally adjusted sales
plot.ts(cbind(ts_wind_speed, wind_speed_d.trend, wind_speed_d.seasonal, wind_speed_d.resid, wind_speed_d.season.adj))
```

```{r}
###### beta = TRUE, gamma = TRUE ######
##### Holt-Winters Filter  #####
out1_1 = HoltWinters(ts_wind_speed, beta = TRUE, gamma = TRUE)
out1_1														# output -- see alpha estimate
out1_1$fitted 										# fitted values in training data
plot(out1_1)											# graph of actual (black) vs fitted (red)
checkresiduals(out1_1)

##### Out of Sample Forecasts
out2_1 = forecast:::forecast.HoltWinters(out1_1, h = 26, level = c(68, 95))	 
# CI with 1 SD and 2SD
plot(out2_1)
```

```{r}
###### beta = FALSE, gamma = TRUE ######
##### Holt-Winters Filter  #####
out1_2 = HoltWinters(ts_wind_speed, beta = FALSE, gamma = TRUE)
# beta=FALSE: no trend; gamma=FALSE: no seasonality
out1_2														# output -- see alpha estimate
out1_2$fitted 										# fitted values in training data
plot(out1_2)											# graph of actual (black) vs fitted (red)
checkresiduals(out1_2)

##### Out of Sample Forecasts
out2_2 = forecast:::forecast.HoltWinters(out1_2, h = 26, level = c(68, 95))	 
# CI with 1 SD and 2SD
plot(out2_2)
```

```{r}
###### beta = FALSE, gamma = FALSE ######
##### Holt-Winters Filter  #####
out1_3 = HoltWinters(ts_wind_speed, beta = FALSE, gamma = FALSE)
# beta=FALSE: no trend; gamma=FALSE: no seasonality
out1_3														# output -- see alpha estimate
out1_3$fitted 										# fitted values in training data
plot(out1_3)											# graph of actual (black) vs fitted (red)
checkresiduals(out1_3)

##### Out of Sample Forecasts
out2_3 = forecast:::forecast.HoltWinters(out1_3, h = 26, level = c(68, 95))	 
# CI with 1 SD and 2SD
plot(out2_3)
```

```{r}
###### beta = TRUE, gamma = FALSE ######
##### Holt-Winters Filter  #####
out1_4 = HoltWinters(ts_wind_speed, beta = TRUE, gamma = FALSE)
# beta=FALSE: no trend; gamma=FALSE: no seasonality
out1_4														# output -- see alpha estimate
out1_4$fitted 										# fitted values in training data
plot(out1_4)											# graph of actual (black) vs fitted (red)
checkresiduals(out1_4)

##### Out of Sample Forecasts
out2_4 = forecast:::forecast.HoltWinters(out1_4, h = 26, level = c(68, 95))	 
# CI with 1 SD and 2SD
plot(out2_4)
```

### Model Selection

For the wind_speed metric, the model with beta = FALSE and gamma = TRUE will be the most suitable one for 3 reasons.

1.  From the graph of actual (black) vs fitted (red), this forecast model performs quite well.
2.  According to the residual plots, the residual checks show similar patterns. However, by carefully evaluating the forecast plots, we conclude the last one is a better fit.
3.  Comparing the plots of the forecasts with different confidence intervals, the second model has a reasonable confidence interval (1-7).

## Metric 5: avg_hours_sun - by Zihan Guo

```{r}
sun = ts(data['avg_hours_sun'], frequency=52, start=c(2015,1))
plot.ts(sun)
```

```{r}
#Decomposition
sun_dec = decompose(sun)
sun_dec.trend = sun_dec$trend
sun_dec.seasonal = sun_dec$seasonal
sun_dec.res = sun_dec$random
sun_dec.season.adj = sun-sun_dec.seasonal
plot.ts(cbind(sun,sun_dec.trend,sun_dec.seasonal,sun_dec.res,sun_dec.season.adj))
```

```{r}
#Holt-Winters Filter
filter1 = HoltWinters(sun,beta=FALSE,gamma=FALSE)
filter2 = HoltWinters(sun,beta=TRUE,gamma=FALSE)
filter3 = HoltWinters(sun,beta=FALSE,gamma=TRUE)
filter4 = HoltWinters(sun,beta=TRUE,gamma=TRUE)
#beta=FALSE,gamma=FALSE
plot(filter1)
out1=forecast:::forecast.HoltWinters(filter1, h = 26, level = c(68, 95))	 
plot(out1)
checkresiduals(filter1)
#beta=TRUE,gamma=FALSE
plot(filter2)
out2=forecast:::forecast.HoltWinters(filter2, h = 26, level = c(68, 95))	 
plot(out2)
checkresiduals(filter2)
#beta=FALSE,gamma=TRUE
plot(filter3)
out3=forecast:::forecast.HoltWinters(filter3, h = 26, level = c(68, 95))	 
plot(out3)
checkresiduals(filter3)
#beta=TRUE,gamma=TRUE
plot(filter4)
out4=forecast:::forecast.HoltWinters(filter4, h = 26, level = c(68, 95))	 
plot(out4)
checkresiduals(filter4)
```

### Model Selection

Choose the one with gamma but without beta, because predictions are negative when using beta, and the model with gamma fits the data better than constant model.
